A Data-Driven Framework for Neural Field Modelling

### 2010-11-03 ltx/first_order_framework/LaTeX_Manuscript.tex
edits to results section

To further study the performance of the proposed framework we used different sets of connectivity basis functions parameters. The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}. For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.

>>>>

To study the robustness of the estimation algorithm, the performance was studied for various connectivity kernels. The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}. By changing the weights of the connectivity kernel we are effectivly changing gain of the system and the range of the field amplitudes. Therefore, we are changing were the

For each subset of parameters the mean of the reconstructed kernel over 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.
